### 2021-11-23 documentos/generators.tex
Iteración 1 de la redacción

There exists a subset of PCE quantum channels that generate 
all PCE's, and the existence of these PCE generators may be explained with 
the vector space point of view.
\janote{Este párrafo lo voy a retocar. El enunciado de arriba es el primer enunciado
del nuevo párrafo. Ojo que hay que introducir la notación $\mcG$.}
By standard theorems of linear algebra, any subspace $W$ can be extended to a
maximal (non-trivial) subspace of dimension $2N-1$ by adjoining appropriate
additional basis elements. This can clearly be done in different ways. We
therefore arrive to the set of maximal extensions of $W$. Clearly, the
intersection of all the elements of this set reduces to $W$ itself, leading to
the result that all PCE's can be obtained as intersections of maximal PCE's. 
\janote{Referenciar \Fref{fig:examplesPCE} y apéndice con una ilustración 
del caso de 2 qubits usando los $\mcG$. Mostrar en ese apéndice todos
los generadores de 2 qubits}
For the case of 1 qubit, the existence of PCE generators $\pceg$ is  
verified by Siudzińska~\cite{siudzinska2019geometry}.
\janote{Esto puede
ser un párrafo, o puede ser un comentario final dentro del párrafo antrerior.}

PCE generators may be characterized with a unique vector index
$\vec\alpha$, and therefore, denoted as $\pceg$. El numero de generadores 
concide con esa vaina. 
PCE generators $\pceg$ may be classified by its local action on 
all individual qubits in the system.
\cpnote{Acuerdate de la referencia a la figura 4}

The matrix $\san$ [see \eref{eq:san}] encodes all the information
of PCE generators $\pceg$ and, therefore, of the PCE quantum channels. \janote{Aquí
tendrá que ir una prueba que aún se está cocinando}

PCE generators $\pceg$ (and so $\san$'s rows and columns) obey a symmetry rule
that defines uniquely every PCE generator.
\cpnote{Acuerdate de otra referencia a la figura 4}

-------------------------------------------------------------------
The set of all PCE quantum channels may be sorted in subsets, 
which we will call equivalence classes, whose
elements are equivalent via particle swaps and local-basis element
permutations. 
\janote{El párrafo que pretendía ser este tendrá que ir en otra parte. 
Aún hay que decidirlo con los demás.}

>>>>

There exists a subset of PCE quantum channels that generate 
all PCE's, and the existence of these PCE generators may be explained with 
the vector space point of view.
%\janote{Este párrafo lo voy a retocar. El enunciado de arriba es el primer enunciado
%del nuevo párrafo. Ojo que hay que introducir la notación $\mcG$.}
By standard theorems of linear algebra, any subspace $W$ [see. \Eref{eq:19}] can be extended to a
maximal (non-trivial) subspace of dimension $2N-1$ by adjoining appropriate
additional basis elements. This can clearly be done in different ways. 
We therefore arrive to the set of maximal extensions of $W$,
where every maximal subspace corresponds to a PCE quantum channel that 
preserves $2^{2N-1}$ (half the) Pauli components $\paulicomponents$ 
of density matrix $\rho$. The
intersection of all the elements of this set reduces to $W$ itself, meaning 
that all PCE's can be obtained as intersections of maximal PCE's, the
PCE generators $\mcG$. Intersections of the maximal subspaces translates into 
compositions of the generators $\mcG$ to obtain any PCE.
Compositions of generators $\mcG$ can be understood intuitively from PCE diagrams
in \Fref{fig:examplesPCE}; the composition of any two 2-qubits PCE generators 
in (c), (d), or (e) is represented by taking the intersection between them both
and the three different possible compositions result in PCE channel in (b).
The existence of the PCE generators $\mcG$ provide the program of 
constructing all PCE channels a tool that avoids the usage of a 
high-computational-cost method. In a moment, we will discuss how to find the 
generators $\mcG$ from matrix $A$, given a symmetry that is obeyed both by the generators 
$\mcG$ and matrix $A$ in \Eref{eq:san}.
%For the case of 1 qubit, the existence of PCE generators $\pceg$ is  
%verified by Siudzińska~\cite{siudzinska2019geometry}.
%\janote{Esto puede
%ser un párrafo, o puede ser un comentario final dentro del párrafo antrerior.}

PCE generators may be identified with a unique vector index
$\vec\alpha$, and thus be denoted as $\pceg$.
% El numero de generadores concide con esa vaina. 
%Let us introduce a convention for the following discussion for 
%the indices in $\vec\alpha$; the number 0 to 3 identifies
Recall that indices $0,1,2,3$ in $\vec\alpha$ correspond to, respectively,
the identity map and the 3 1-qubit PCE quantum channels that project the 
Bloch sphere to the rectangular axes $x$, $y$ and $z$. 
Therefore we will correspond every PCE generator to a collection of numbers 
that tells what its local-action is on every individual qubit in the system.
All of this collections of numbers happen to be all vector indices $\{\valpha\}$.
For example, the PCE generator represented in \Fref{fig:examplesPCE}(c),
whose local-action on the first qubit (first column) is to project the corresponding local Bloch sphere 
to the $x$ axis and on the second qubit (first row) to map the corresponding
local Bloch sphere to itself, may be characterized with the vector index (1,0). 
Then, it is clear that in general one can associate a unique $\vec\alpha$ to 
every PCE generator and so denote them as $\pceg$.

PCE generators $\pceg$ obey a symmetry
that defines uniquely every PCE generator. The coefficients  $\{\taus\}$ of every 
generator $\pceg$ arranged in a hypercubic $N$-dimensional array 
%of dimensions $\underbrace{4\times 4\times\ldots\times 4}_{N}$ 
obey a symmetry with respect to the $N$ hyperplanes of dimension $N-1$
\janote{según wikipedia, por definición, los hiperplanos son de dimensión 
$N-1$. Así que podría quitarse la aclaración de la dimensión. Lo dejo así y 
espero retroalimentación} 
that separate the array into two half arrays \janote{No estoy tan satisfecho con la redacción de este enunciado}.
See, in \Fref{fig:examplesPCE}, that generators $\mcG_{(1,3)}$, $\mcG_{(3,2)}$
and $\mcG_{(2,2)}$ represented in (c), (d) and (e), respectively,
are either symmetric or anti-symmetric with respect to the lines that cut vertically 
and horizontally in half the diagrams. In fact, this symmetry may be used to
construct all generators $\pceg$ as follows. Start out with $\tau_{0,\ldots,0}=1$
and begin to ``unfold'' the array of all $\pceg$'s coefficients $\taus$ by deciding
whether $\tau_{0,\ldots,0,1}$ be set to 1 or 0 (symmetric or anty-simmetric with 
respect to $\tau_{0,\ldots,0}$), then choose the values of $\{\tau_{0,\ldots,0,2}, 
\tau_{0,\ldots,0,3}\}$ to be symmetric or anti-symmetric with respect to 
$\{\tau_{0,\ldots,0},\tau_{0,\ldots,0,1}\}$; you need to keep this procedure 
for the remaining subsets with $2l$ coefficients $\taus$, with $l$ the cardinality of 
the previous subset, by setting the coefficients $\taus=0,1$ in order to be symmetric or
anti-symmetric to the previous subset. For example, let us illustrate the 
procedure to construct $\mcG_{(3,2)}$ represented in \Fref{fig:examplesPCE}(d).
One starts out choosing the value of $\tau_{(0,1)}$ to be anti-symmetric to $\tau_{(0,0)}$, then one chooses 
$\qty{\tau_{(0,2)},\tau_{(0,3)}}$ symmetric to $\qty{\tau_{(0,0)},\tau_{(0,1)}}$,
$\qty{\tau_{(1,0)},\tau_{(1,1)},\tau_{(1,2)},\tau_{(1,3)}}$ anti-symmetric 
to $\qty{\tau_{(0,0)},\tau_{(0,1)},\tau_{(0,2)},\tau_{(0,3)}}$, and finally
the last eight components $\tau_{\vec\alpha}$ anti-symmetric to the first 
eight.

The matrix $\san$ [see \eref{eq:san}] encodes all the information
of PCE generators $\pceg$ and, therefore, of all PCE quantum channels. 
The rows and columns of matrix $A$ also obey the symmetry previously discussed 
for PCE generators $\pceg$. It suffices to check that rows and columns of matrix $a$
in \Eref{eq:1} obey the aforementioned symmetry when they are arranged in a hypercubic 
$N$-dimensional array of order $4$.
As a consequence of $a$'s elements being $\pm1$, the power tensor $a^{\otimes N}$ will hold the symmetry of the 
rows and columns of $A$. 
Therefore, this establishes a deep connection between the matrix $A$ and 
PCE quantum channels. It allows one to infer the PCE generators $\pceg$
by taking its corresponding coefficients $\{\taus\}$ as the rows or columns of $A$ 
after taking $-1\mapsto0$. In \appref{sec:2_qubits} we illustrate this program 
for 2-qubits PCE channels.
In short, it is sufficient to have the matrix $A$ to construct 
all PCE quantum channels.
%\janote{Aquí
%tendrá que ir una prueba que aún se está cocinando}

- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -

The set of all PCE quantum channels may be sorted in subsets, 
which we will call equivalence classes, whose
elements are equivalent via particle swaps and local-basis element
permutations. 
\janote{El párrafo que pretendía ser este tendrá que ir en otra parte. 
Aún hay que decidirlo con los demás.}
